Describe and Explore: Using feature-based time-series clustering to understand modern intensive longitudinal data (Working Title)

### 2022-11-30 manuscript.tex
:sparkles: figs added
:pnecil2: typo
Updates from Overleaf
:sparkles: migration example intro

\section{Empirical Illustration}
To illustrate common use cases of feature-based time series clustering with psychological ESM data, we apply the clustering process to a recent set of studies that collected diverse concepts with context-specific measurements. The illustration ...

\hl{Move migration experience literature background here ...}

% Methods and Results from RMarkdown render
\input{methods-and-results}
\input{tables/descrWide.tex}

@@

\subsection{Migration Parts}
One example of this phenomenon has been the cultural adaptation literature, where researchers have started using ESM data to follow the daily interactions of migrants with the local majority \citep[e.g.,][]{Kreienkamp2022b}.

As an example, within the cultural adaptation literature, prominent reviews have called for more longitudinal \citep[e.g.,][]{Ward2019} and real-world data \citep[e.g.,][]{McKeown2017}, while at the same time conceptual works have pushed for more comprehensive assessments of human experiences, including motivational, affective, cognitive, and behavioral aspects \citep[e.g.,][]{Kreienkamp2022d}.

In the example of the migration experiences, researchers might for example be interested in how well-being develops in relations the quality of interactions with the majority group. Because rating of interaction quality are only possible when an interaction actually happened, one cannot impute interaction quality ratings for measurements that did not include an interaction.

@@

\begin{figure*}[hbtp]
  \caption{Exemplary Flowchart of Data Points in Feature-Based Time Series Clustering}
  \label{fig:TSCFlowN}
  \centering\includegraphics[width=\textwidth]{figures/TS Cluster Flow/tsClustFlowN.pdf}
  \caption*{Note: \\
  The presented number of participants, variables, and measurement occasions are somewhat arbitrary but generally represent common sample sizes found within the literature. Also the number of extracted clusters is presented for illustrative purposes only}
\end{figure*}

>>>>

\section{Empirical Illustration}
To illustrate common use cases of feature-based time series clustering with psychological ESM data, we apply the clustering process to a recent set of studies that collected diverse concepts with context-specific measurements. The illustration specifically uses data from research on migration experiences, where researchers have started using ESM data to follow the daily interactions of migrants with the cultural majority groups \citep[e.g.,][]{Keil2020}. This new type of research comes as a response to prominent reviews, which have called for more longitudinal \citep[e.g.,][]{Ward2019} and real-world data \citep[e.g.,][]{McKeown2017}. At the same time, conceptual works have pushed for more diverse assessments of migration experiences, including motivational, affective, cognitive, and behavioral aspects \citep[e.g.,][]{Kreienkamp2022d}. The migration ESM research, thus, offers a good example of the modern ESM data that introduces diverse conceptualizations and more event-specific missingness patterns.

% Methods and Results from RMarkdown render
\input{methods-and-results}
%\input{tables/descrWide}
\input{tables/descrLong}

@@

\subsection{Migration Parts}
In the example of the migration experiences, researchers might for example be interested in how well-being develops in relations the quality of interactions with the majority group. Because rating of interaction quality are only possible when an interaction actually happened, one cannot impute interaction quality ratings for measurements that did not include an interaction.

@@

\begin{figure*}[hbtp]
  \caption{Exemplary Flowchart of Data Points in Feature-Based Time Series Clustering}
  \label{fig:TSCFlowN}
  \centering\includegraphics[width=\textwidth]{figures/TS Cluster Flow/tsClustFlowN.pdf}
  \caption*{Note: \\
  The presented number of participants, variables, and measurement occasions are somewhat arbitrary but generally represent common sample sizes found within the literature. Also the number of extracted clusters is presented for illustrative purposes only.}
\end{figure*}

\begin{figure*}[hbtp]
  \caption{Cluster Group Comparisons based on Features and Variables}
  \label{fig:clusterFeatVar}
  \centering\includegraphics[width=\textwidth]{figures/clusterFeatVarComb.pdf}
  \caption*{Note: \\
  same data}
\end{figure*}

\begin{figure*}[hbtp]
  \caption{Cluster Group Comparisons over time}
  \label{fig:clusterTs}
  \centering\includegraphics[width=\textwidth]{figures/clusterTsComb.pdf}
  \caption*{Note: \\
  same data}
\end{figure*}
